Carbonate chemistry at Ny-Ålesund

### 2021-12-13 awipev-CO2.Rmd
ading seafet calibration with 9m depth taken in consideration only

```{r read observatory data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- as_tsibble(d_hour, index = datetime) %>% #d_all will be the merger
  tsibble::fill_gaps(.full=TRUE)
d_hour$date <-  as.Date(d_hour$datetime, format="%Y-%m-%d")

d_hour <- d_hour %>%
  dplyr::filter(datetime <= as.POSIXct("2021-01-10")) %>% #cutoff date
  dplyr::select(-pco2_inst) %>% # this is the serial number of pCO2 sensor, not needed
  dplyr::rename(
    pco2_fb = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  # data post 2020-03-01 eliminated because no maintenance and lots of algae
  dplyr::mutate(pco2_fb = ifelse(datetime >= as.POSIXct("2020-03-01 00:00"), NA, pco2_fb)) %>%
  arrange(datetime)

# read a file provided by Philipp on 2021-04-09 which fills most gaps of pressure data
# depth_complete replaces all other depth and pressure variables
svl_remos_depth <- tibble(
  readRDS(file = paste0(
    path,
    "fb_data/svl_remos_depth.rds"
  ))) %>% 
  dplyr::select(-adcp_fill, -ctd_fill)

d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
  dplyr::mutate(depth = ifelse(!is.na(pressure_insitu_ctd), pressure_insitu_ctd, depth_complete))

# check_plot <- d_hour %>% 
#   ggplot() + geom_point(aes(x=datetime, y=depth, col='blue', alpha = 0.7)) +
#   geom_point(aes(x=datetime, y=depth, col='red', alpha = 0.3))

@@

d_all <- d_hour %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group = as.factor(dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
                depth > 2 & depth <= 4 ~ '2-4',
                depth > 4 & depth <= 6 ~ '4-6',
                depth > 6 & depth <= 8 ~ '6-8',
                depth > 8 & depth <= 12 ~ '>8', #8 to 12.4
                TRUE ~ 'NA'
                )),
                sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
                sal_insitu_ctd_3m = ifelse(depth_group == '2-4', sal_insitu_ctd, NA),
                sal_insitu_ctd_5m = ifelse(depth_group == '4-6', sal_insitu_ctd, NA),
                sal_insitu_ctd_7m = ifelse(depth_group == '6-8', sal_insitu_ctd, NA),
                sal_insitu_ctd_10m = ifelse(depth_group == '>8', sal_insitu_ctd, NA),
                temp_insitu_ctd_1m = ifelse(depth_group == '0-2', temp_insitu_ctd, NA),
                temp_insitu_ctd_3m = ifelse(depth_group == '2-4', temp_insitu_ctd, NA),
                temp_insitu_ctd_5m = ifelse(depth_group == '4-6', temp_insitu_ctd, NA),
                temp_insitu_ctd_7m = ifelse(depth_group == '6-8', temp_insitu_ctd, NA),
                temp_insitu_ctd_10m = ifelse(depth_group == '>8', temp_insitu_ctd, NA),
  ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    temp_insitu_ctd_1m,
    temp_insitu_ctd_3m,
    temp_insitu_ctd_5m,
    temp_insitu_ctd_7m,
    temp_insitu_ctd_10m
  )
), na.rm = TRUE)) %>% 
  ungroup()

#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) ,
                hour = lubridate::hour(d_hour$datetime)# abbreviated months
  )
d_all <- d_all %>% 
  dplyr::select(order(colnames(d_all)))
rm(d_hour)

@@

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m))
```

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_10m
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m))
```

@@

# interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp10m ctd)
tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
names(tempmixinterp) <- c("datetime", "temp_mix_interp")
tempmixinterp <- as.data.frame(tempmixinterp)
d_all$temp_mix_interp <- tempmixinterp$temp_mix_interp

@@

# Make mean for replicates + SD
pH_seafet_mean <- pH_seafet %>%
  dplyr::select(datetime, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_4_mean = mean(ph_s_sf_temp_4, na.rm = TRUE)
                   )
pH_durafet_mean <- pH_durafet %>%
  dplyr::select(datetime, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE))

@@

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_mix_interp ,sal_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_mix,temp_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    sal_mix_interp = mean(sal_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_mix_interp = mean(temp_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
  )

@@

#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(29, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean10m = mean(sal_insitu_ctd_10m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
  ungroup()

p_sal_range <- ggplot(data = df) +
  geom_histogram((aes(x = range))) +
  labs(title = "Daily salinity difference between 1 and 10 m", x = "Difference") +
  Mytheme(size_labs = 8)
p_sal_range

kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
rm(sal_xts)
```
Extreme differences: `r dplyr::filter(df, range < -3 | range > 2)`.

There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m). The salinity difference between 1 and 10 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`). The difference with depth is therefore significant.

### **Sal FB / Sal CTD 10 m **

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_10m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_10m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 10 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

d_all$diff_sal_fb_insitu_10m <- d_all$sal_insitu_ctd_10m - d_all$sal_fb
mean_diff_sal_fb_insitu_10m <- round(mean(d_all$diff_sal_fb_insitu_10m, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu_10m <- round(sd(d_all$diff_sal_fb_insitu_10m, na.rm = TRUE), digits = 2)
```

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_10m` ± `r sd_diff_sal_fb_insitu_10m` PSU.

@@

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 10m)
- 1 fixed at 11 meters depth (temp_insitu_11m)

@@

### **Temperature profiles**
```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m)
temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
dyLegend(show = "follow")   %>%
dyAxis("y",valueRange = c(-2, 10)) %>%
dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
            mean10m = mean(temp_insitu_ctd_10m, na.rm = TRUE),
            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_10m, na.rm = TRUE)) %>% 
  ungroup()
rm(temp_xts)
```
There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)`°C and `r max(df$range, na.rm=TRUE)`°C (mean: `r mean(df$range, na.rm=TRUE)`°C; `r median(df$range, na.rm=TRUE)`°C). The difference with depth is therefore significant.

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_10m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_10m, y= temp_insitu_11m, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_10m
mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
```

@@

>>>>

```{r read observatory data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- as_tsibble(d_hour, index = datetime) %>%#d_all will be the merger
  tsibble::fill_gaps(.full=TRUE)
d_hour$date <-  as.Date(d_hour$datetime, format="%Y-%m-%d")

d_hour <- d_hour %>%
  dplyr::filter(datetime <= as.POSIXct("2021-01-10")) %>% #cutoff date
  dplyr::select(-pco2_inst) %>% # this is the serial number of pCO2 sensor, not needed
  dplyr::rename(
    pco2_fb = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  # data post 2020-03-01 eliminated because no maintenance and lots of algae
  dplyr::mutate(pco2_fb = ifelse(datetime >= as.POSIXct("2020-03-01 00:00"), NA, pco2_fb)) %>%
  arrange(datetime)
# read a file provided by Philipp on 2021-04-09 which fills most gaps of pressure data
# depth_complete replaces all other depth and pressure variables
svl_remos_depth <- tibble(
  readRDS(file = paste0(
    path,
    "fb_data/svl_remos_depth.rds"
  )))
d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
  dplyr::select(-adcp_fill, -ctd_fill) %>% 
  dplyr::rename(depth = depth_complete)
# check_plot <- d_hour %>% 
#   ggplot() + geom_point(aes(x=datetime, y=depth, col='blue', alpha = 0.7)) +
#   geom_point(aes(x=datetime, y=depth, col='red', alpha = 0.3))

@@

d_all <- d_hour %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    temp_insitu_ctd_1m,
    temp_insitu_ctd_3m,
    temp_insitu_ctd_5m,
    temp_insitu_ctd_7m,
    temp_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) ,
                hour = lubridate::hour(d_hour$datetime)# abbreviated months
  )
rm(d_hour)

@@

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
```

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

@@

# interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp9m ctd)
tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
names(tempmixinterp) <- c("datetime", "temp_mix_interp")
tempmixinterp <- as.data.frame(tempmixinterp)
d_all$temp_mix_interp <- tempmixinterp$temp_mix_interp

@@

   )
# Make mean for replicates + SD
pH_seafet_mean <- pH_seafet %>%
  dplyr::select(datetime, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
                   ph_s_sf_temp_4_mean = mean(ph_s_sf_temp_4, na.rm = TRUE)
                   )
pH_durafet_mean <- pH_durafet %>%
  dplyr::select(datetime, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE))

@@

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  group_by(datetime) %>%
#dplyr::select( datetime, date,hour,sal_fb,sal_mix_interp ,sal_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_mix,temp_mix_interp,temp_insitu_11m) %>%
  summarise(datetime = mean(datetime, na.rm = TRUE),
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    sal_mix_interp = mean(sal_mix_interp, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
     temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_mix_interp = mean(temp_mix_interp, na.rm = TRUE),
        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'

@@

#SAL CTD profile
sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()

p_sal_range <- ggplot(data = df) +
  geom_histogram((aes(x = df$range))) +
  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
  Mytheme(size_labs = 8)
p_sal_range

kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
rm(sal_xts)
```
There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m). The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`). The difference with depth is therefore significant.

### **Sal FB / Sal CTD 9 m **

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
```

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.

@@

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
- 1 fixed at 11 meters depth (temp_insitu_11m)

@@

### **Temperature profiles**
```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
dyLegend(show = "follow")   %>%
dyAxis("y",valueRange = c(-2, 10)) %>%
dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
            mean9m = mean(temp_insitu_ctd_9m, na.rm = TRUE),
            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_9m, na.rm = TRUE)) %>% 
  ungroup()
rm(temp_xts)
```
There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)`°C and `r max(df$range, na.rm=TRUE)`°C (mean: `r mean(df$range, na.rm=TRUE)`°C; `r median(df$range, na.rm=TRUE)`°C). The difference with depth is therefore significant.

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_9m
mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
```

@@

### add the depth into discrete df. In order to see where the seafet was.
discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth, depth_discrete),by="closest_datetime")
discrete <- discrete%>%dplyr::filter(discrete$datetime < "2021-07-01 00:00:00")

offset_xts <- select(discrete, closest_datetime, depth,depth_discrete, ph_s_sf_temp_insi)
offset_xts <- as.xts(offset_xts, order.by=offset_xts$closest_datetime)
